%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV LaTeX Template for CV/Resume
%
% This template has been downloaded from:
% https://github.com/posquit0/Awesome-CV
%
% Author:
% Claud D. Park <posquit0.bj@gmail.com>
% http://www.posquit0.com
%
%
% Adapted to be an Rmarkdown template by Mitchell O'Hara-Wild
% 23 November 2018
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%
%-------------------------------------------------------------------------------
% CONFIGURATIONS
%-------------------------------------------------------------------------------
% A4 paper size by default, use 'letterpaper' for US letter
\documentclass[11pt, a4paper]{awesome-cv}

% Configure page margins with geometry
\geometry{left=1.4cm, top=.8cm, right=1.4cm, bottom=1.8cm, footskip=.5cm}

% Specify the location of the included fonts
\fontdir[fonts/]

% Color for highlights
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight

\definecolor{awesome}{HTML}{414141}

% Colors for text
% Uncomment if you would like to specify your own color
% \definecolor{darktext}{HTML}{414141}
% \definecolor{text}{HTML}{333333}
% \definecolor{graytext}{HTML}{5D5D5D}
% \definecolor{lighttext}{HTML}{999999}

% Set false if you don't want to highlight section with awesome color
\setbool{acvSectionColorHighlight}{true}

% If you would like to change the social information separator from a pipe (|) to something else
\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad}

\def\endfirstpage{\newpage}

%-------------------------------------------------------------------------------
%	PERSONAL INFORMATION
%	Comment any of the lines below if they are not required
%-------------------------------------------------------------------------------
% Available options: circle|rectangle,edge/noedge,left/right

\name{John E. Scofield, M.S.}{}

\address{Columbia, Missouri}

\email{\href{mailto:jel7c5@mail.missouri.edu}{\nolinkurl{jel7c5@mail.missouri.edu}}}
\github{scofieldjohn}
\twitter{jscofield24}

% \gitlab{gitlab-id}
% \stackoverflow{SO-id}{SO-name}
% \skype{skype-id}
% \reddit{reddit-id}


\usepackage{booktabs}

% Templates for detailed entries
% Arguments: what when with where why
\usepackage{etoolbox}
\def\detaileditem#1#2#3#4#5{%
\cventry{#1}{#3}{#4}{#2}{\ifx#5\empty\else{\begin{cvitems}#5\end{cvitems}}\fi}\ifx#5\empty{\vspace{-4.0mm}}\else\fi}
\def\detailedsection#1{\begin{cventries}#1\end{cventries}}

% Templates for brief entries
% Arguments: what when with
\def\briefitem#1#2#3{\cvhonor{}{#1}{#3}{#2}}
\def\briefsection#1{\begin{cvhonors}#1\end{cvhonors}}

\providecommand{\tightlist}{%
	\setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}

%------------------------------------------------------------------------------




\begin{document}

% Print the header with above personal informations
% Give optional argument to change alignment(C: center, L: left, R: right)
\makecvheader

% Print the footer with 3 arguments(<left>, <center>, <right>)
% Leave any of these blank if they are not needed
% 2019-02-14 Chris Umphlett - add flexibility to the document name in footer, rather than have it be static Curriculum Vitae
\makecvfooter
  {October, 2020}
    {John E. Scofield, M.S.~~~·~~~Curriculum Vitae}
  {\thepage}


%-------------------------------------------------------------------------------
%	CV/RESUME CONTENT
%	Each section is imported separately, open each file in turn to modify content
%------------------------------------------------------------------------------



An \textbf{online version} of this CV can be viewed at: \url{https://jscofield.org/}

\hypertarget{education}{%
\section{Education}\label{education}}

\detailedsection{\detaileditem{Ph.D. Candidate - Cognition \& Neuroscience}{Fall 17 - Fall 20}{University of Missouri}{Columbia, MO}{\item{Advisors: Jeffrey Johnson, Ph.D. - David Geary, Ph.D.}}\detaileditem{M.S. - Experimental Psychology}{Fall 15 - Spring 17}{Missouri State University}{Springfield, MO}{\item{Advisor: Bogdan Kostic, Ph.D.}}\detaileditem{Graduate Certificate - Statistics and Research Design}{Fall 15 - Spring 17}{Missouri State University}{Springfield, MO}{\item{A supplementary certificate in tandem with a Master of Science degree}\item{targeting advanced statistical techniques and applied research areas. Advisor: Erin Buchanan, Ph.D.}}\detaileditem{B.S. - Psychology}{Fall 13 - Spring 15}{Truman State University}{Kirksville, MO}{\item{Advisor: Professor Salvatore Costa}}}

\hypertarget{teaching}{%
\section{Teaching}\label{teaching}}

A copy of my teaching philosophy is accessible online at: \url{https://jscofield.org/}

\detailedsection{\detaileditem{Instructor}{Fall 20}{PSYCH2820: Minds, Brains, \& Machines}{University of Missouri}{\item{cognitive neuroscience and its relation to the developing field of artificial intelligence}}\detaileditem{Instructor}{Summer 19}{PSYCH3010: Research Methods}{University of Missouri}{\item{Online instruction following fundamentals of research in psychology}}\detaileditem{Guest Lecture}{Summer 18}{PSYCH3010: Research Methods}{University of Missouri}{\item{Overviews of neuroscientific tools in neuroscience}\item{measurement, reliablility, validity (EEG, fMRI, TMS, MEG)}}\detaileditem{Instructor}{Fall 15 - Spring 17}{PSY302: Experimental Psychology}{Missouri State University}{\item{Laboratory course with a strong lecture component. }\item{Demonstrations and discussions of classic experiments}\item{Oversaw research projects (from data collection to manuscript writeups)}}\detaileditem{Teacher's Assistant}{Spring 18 - Fall 19}{PSYCH3010: Research Methods}{University of Missouri}{\item{distribution of course content and grading}}\detaileditem{Teacher's Assistant}{Fall 17}{PSYCH2410: Developmental Psychology}{University of Missouri}{\item{distribution of course content and grading}}\detaileditem{Teacher's Assistant}{Fall 17}{PSYCH3420: Cognitive Development in Childhood}{University of Missouri}{\item{distribution of course content and grading}}}

\hypertarget{publications}{%
\section{Publications}\label{publications}}

\hypertarget{submitted}{%
\subsection{Submitted ------------------------------------------------------------------------------}\label{submitted}}

Geary, D. C., \textbf{Scofield, J. E.}, Hoard, M. K., \& Nugent, L. (\emph{Revise \& Resubmit}). Boys' advantage on the fractions number line is mediated by visuospatial attention: Evidence for a parietal-spatial contribution to number line learning.

\textbf{Scofield, J. E.}, \& Johnson, J. D. (\emph{Revise \& Resubmit}). The diminishing precision of memory for time.

Geary, D. C., \textbf{Scofield, J. E.}, Hoard, M. K., \& Nugent, L. (\emph{Revise \& Resubmit}). Cognitive, attitudinal, and classroom contributions to variation in the pattern of adolescents' mathematical competencies.

\hypertarget{section}{%
\subsection{2020 -----------------------------------------------------------------------------------}\label{section}}

Hone, L. S. E., \textbf{Scofield, J. E.}, Bartholow, B. D., \& Geary, D. C. (\emph{In Press}). Binge drinking is associated with sex-specific cognitive deficits. \emph{Evolutionary Psychology}. \url{doi:10.1177/1474704920954445} preprint: \url{https://psyarxiv.com/m3xa8}

Geary, D. C., Hoard, M. K., Nugent, L., \& \textbf{Scofield, J. E.} (2020). In-class attention, spatial ability, and mathematics anxiety predict across-grade gains in adolescents' mathematics achievement. \emph{Journal of Educational Psychology}. \url{doi:10.1037/edu0000487}

\textbf{Scofield, J. E.}, Price, M. H., Flores, A., Merkle, E. C., \& Johnson, J. D. (2020). Repetition attenuates the influence of recency on recognition memory: Behavioral and electrophysiological evidence. \emph{Psychophysiology}, \emph{57}(9), e13601. \url{doi:10.1111/PSYP.13601}. \url{https://osf.io/572jt/}

\hypertarget{section-1}{%
\subsection{2019 -----------------------------------------------------------------------------------}\label{section-1}}

Hone, L. S. E., \textbf{Scofield, J. E.}, Bartholow, B. D., \& Geary, D. C. (2019). Tutorial on designing, implementing, and analyzing a degraded image paradigm: A facial expression-decoding task example. \emph{The Quantitative Methods for Psychology}, \emph{15}(3), 200-213. doi: 10.20982/tqmp.15.3.p200. \url{https://osf.io/ntmah/}

Cowan, N., Adams, E. J., Bhangal, S., Corcoran, M., Decker, R., Dockter, C. E., \ldots{} \textbf{Scofield, J. E.}, \ldots{} \& Watts, A. L. (2019). Foundations of arrogance: A broad survey and framework for research. \emph{Review of General Psychology}, \emph{23}(4), 425-443. \url{doi:10.1177/1089268019877138}.

Chu, F. W., vanMarle, K., Hoard, M. K., Nugent, L., \textbf{Scofield, J. E.}, \& Geary, D. C. (2019). Preschool deficits in cardinal knowledge and executive function contribute to longer-term mathematical learning disabilities. \emph{Journal of Experimental Child Psychology}, \emph{188}, 104668. doi: 10.1016/j.jecp.2019.104668. \url{https://osf.io/phtxm/}

\textbf{Scofield, J. E.}, Johnson, J. D., Wood, P. K., \& Geary, D. C. (2019). Latent resting-state network dynamics in boys and girls with attention-deficit/hyperactive disorder. \emph{PLOS ONE}, \emph{14}(6), e0128891. \url{doi:10.1371/journal.pone.0218891}. \url{https://osf.io/xqewf/}

Geary, D. C., Hoard, M. K., Nugent, L., Chu, F., \textbf{Scofield, J. E.}, \& Hibbard, D. F. (2019). Sex differences in mathematics anxiety and attitudes: Concurrent and longitudinal relations to mathematical competence. \emph{Journal of Educational Psychology}. \url{doi:10.1037/edu0000355}.

\textbf{Scofield, J. E.}, Kostic, B., \& Buchanan, E. M. (2019). How the presence of others affects desirability judgments in heterosexual and homosexual participants. \emph{Archives of Sexual Behavior}. \url{doi:10.1007/s10508-019-01516-w}. \url{https://osf.io/ej5kh/}

Valentine, K. D., Buchanan, E. M., \textbf{Scofield, J. E.}, \& Beauchamp, M. T. (2019). Beyond p-values: Utilizing multiple estimates to evaluate evidence. \emph{Behaviormetrika}. \url{doi:10.1007/s41237-019-00078-4}.

Buchanan E., Gillenwaters A., \textbf{Scofield J. E.}, Valentine K. (2019). MOTE: Measure of the Effect: Package
to assist in effect size calculations and their confidence intervals. R package version 1.0.1, \url{https://cran.r-project.org/web/packages/MOTE/index.html}

\hypertarget{section-2}{%
\subsection{2018 -----------------------------------------------------------------------------------}\label{section-2}}

Buchanan, E. M., \& \textbf{Scofield, J. E.} (2018). Methods to detect low quality data and its implication for psychological research. \emph{Behavior Research Methods}, 50(6), 2586-2596. \url{doi:10.3758/s13428-018-1035-6}.

\textbf{Scofield, J. E.}, Buchanan, E. M., \& Kostic, B. (2018). A meta-analysis of the survival processing advantage in memory. \emph{Psychonomic Bulletin and Review}, 25(3), 997-1012. \url{doi:10.3758/s13423-017-1346-0}.

\hypertarget{section-3}{%
\subsection{2017 ------------------------------------------------------------------------------------}\label{section-3}}

Derringer, C. J., \textbf{Scofield, J. E.}, \& Kostic, B. (2017). Investigations of a reproductive processing advantage in memory. \emph{Memory and Cognition}, 45(6), 983-1001. doi: 10.3758/s13421-017-0709-0.

\hypertarget{pre-printsreplications}{%
\subsection{Pre-prints/Replications ------------------------------------------------------------}\label{pre-printsreplications}}

Sumner, C., \textbf{Scofield, J. E.}, Buchanan, E. M., Evans, M., \& Shearing, M. (2019). The role of personality, authoritarianism and cognition in the United Kingdom's 2016 referendum on European union membership. \url{https://osf.io/n5r67/}

Kostic, B., \& \textbf{Scofield, J. E.} (2019). Sex differences across sexual orientation and sexual identity. \url{https://osf.io/8tnd4/}

Buchanan, E. M., \textbf{Scofield, J. E.}, \& Nunley, N. (2018). The N400's 3 As: Association, automaticity, attenuation (and some semantics too). \url{https://osf.io/6w2se/}

Buchanan, E. M., \& \textbf{Scofield, J. E.} (2018). Bulletproof bias? Considering the type of data in common proportion of variance effect sizes. \url{https://osf.io/cs4vy/}

\textbf{Scofield, J. E.} \& Kostic, B. (\emph{2016, April 05}). Eye movements and handedness in memory. Retrieved from \url{http://www.PsychFileDrawer.org/replication.php?attempt=MjQ2}

\textbf{Scofield, J. E.} \& Kostic, B. (\emph{2016, January 29}). Sex and sexual orientation differences in mating.
Retrieved from \url{http://www.psychfiledrawer.org/replication.php?attempt=MjM4}

\hypertarget{presentations}{%
\section{Presentations}\label{presentations}}

Clocksin, H. E., \textbf{Scofield, J. E.}, Beversdorf, D. Q., Riecken, C., Christ, S. E., \& Johnson, J. D. (2020, May). \emph{Resting-state functional connectivity differences in memory networks of autism spectrum disorder}. Poster presented at the Cognitive Neuroscience Society Annual Meeting, Virtual (Boston, MA).

\textbf{Scofield, J. E.}, \& Johnson, J. D. (2020, May). \emph{The diminishing precision of temporal information in episodic memory retrieval}. Poster presented at the Cognitive Neuroscience Society Annual Meeting, Virtual (Boston, MA).

\textbf{Scofield, J. E.}, \& Johnson, J. D. (2019, November). \emph{The precision of retrieving temporal information associated with episodic memories}. Poster presented at the Psychonomic Society Annual Meeting, Montreal, Canada.

Hone, L. S. E., \textbf{Scofield, J. E.}, Bartholow, B. D., \& Geary, D. C. (2019, June). \emph{Development of a timed facial expression decoding task}. Talk presented at teh NorthEastern Evolutionary Psychology Society, Boston, MA.

Shenk, M., McAllister, L., \textbf{Scofield, J. E.}, Zoeller, M., \& Jaeggi, A. (2019 June). \emph{Are reproductive behaviors sensitive to priming? A bayesian multi-level meta-analysis}. Talk presented at the Human Behavior \& Evolution Society Annual Meeting, Boston, MA.

\textbf{Scofield, J. E.}, Price, M. H., Flores, A., Merkle, E. C., \& Johnson, J. D. (2019, March). \emph{Behavioral and electrophysiological correlates of the memory search process during continuous recognition}. Poster presented at the Cognitive Neuroscience Society, San Francisco, CA.

\textbf{Scofield, J. E.}, Price, M. H., Flores, A., Merkle, E.C., \& Johnson, J.D. (2018, November). \emph{Scanning through memory along a compressed timeline: A continuous recognition task with multiple repetitions}. Poster presented at the Psychonomic Society Annual Meeting, New Orleans, LA.

\textbf{Scofield, J. E.} \& Geary, D. C. (2018, August). \emph{Sex differences in brain network dynamics across time}. Oral talk presented at the Heterodox Psychology Workshop, Orange, CA.

\textbf{Scofield, J. E.} (2018, May). \emph{The contribution of handedness to hippocampal functional connectivity}. Data blitz presented at the Show Me State Conference on Cognition, St.~Louis, MO.

\textbf{Scofield, J. E.}, \& Johnson, Jeffrey D. (2018, March). \emph{Resting-state hippocampal functional connectivity depends on handedness}. Poster presented at the Cognitive Neuroscience Society, Boston, MA.

\textbf{Scofield, J. E.}, \& Buchanan, E. M. (2017, November). \emph{Survey automation detection methods and its implications on psychological research}. Oral talk presented at the Society for Computers in Psychology Conference, Vancouver, BC, Canada.

Buchanan, E. M., \textbf{Scofield, J. E.}, \& Marshall, C. Z. (2017, November). \emph{Distributions and Sampling Variance for Five Effect Size Measures of Variance Overlap}. Poster presented at the Psychonomic Society Annual Meeting, Vancouver, BC, Canada.

\textbf{Scofield, J. E.}, Buchanan, E. M., \& Kostic, B. (2016, November). \emph{A meta-analysis of the survival processing advantage in memory}. Poster presented at the Psychonomic Society Annual Meeting, Boston, MA.

Decker, R., \textbf{Scofield, J. E.}, Wekesser, M., Myers, A., \& Palmer, T. (2016, May). \emph{Flash suppression eliminates lip-movement influence in syllable identification}. Poster presented at the Midwestern Psychological Association Conference, Chicago, IL.

\textbf{Scofield, J. E.} (2016, April). \emph{Sex differences in gender, orientation, and identity}. Poster presented at the Missouri State University Interdisciplinary Forum, Springfield, MO.

\textbf{Scofield, J. E.}, \& Kostic, B. (2016, April). \emph{Sex differences in heterosexual, homosexual, and bisexual participants}. Oral Talk presented at the Southwestern Psychological Association Conference, Dallas, TX.

\hypertarget{research-experience}{%
\section{Research Experience}\label{research-experience}}

\detailedsection{\detaileditem{University of Missouri}{Fall 17 - Current}{Memory and Neuroimaging Lab}{Columbia, MO}{\item{co-investigator and research assistant to Dr. Jeffrey Johnson.}\item{Investigates Episodic Memory using fMRI \& EEG.}\item{Incorporating both univariate (GLM) and multivariate (MVPA; machine learning) approaches}}\detaileditem{University of Missouri}{Fall 17 - Current}{Evolution and Cognitive Development Lab}{Columbia, MO}{\item{co-investigator and research assistant to Dr. David Geary}\item{Incorporates sexuals selection theory to investigate human cognitive sex differences}}\detaileditem{Missouri State University}{Spring 16 - Fall 18}{DOOM Research Lab}{Springfield, MO}{\item{Research assistant to Dr. Erin Buchanan.}\item{Statistical techniques including simulations, effect sizes, and traditional parametric vs. Bayesian techniques}}\detaileditem{Missouri State University}{Fall 15 - Spring 17}{Cognitive Research Lab}{Springfield, MO}{\item{co-investigator and assistant to Dr. Bogdan Kostic}\item{Investigated common cognitive phenomena as well as human sex differences}}\detaileditem{Truman State University}{Fall 13 - Spring 15}{Cognition Lab}{Kirksville, MO}{\item{research assistant to Dr. Terry Palmer}\item{investigating the role of consciousness in multisensory integration}}\detaileditem{Truman State University}{Fall 14 - Spring 15}{Psychological Testing Lab}{Kirksville, MO}{\item{research assistant to professor Salvatore Costa}}}

\hypertarget{statistical-analysis-skills}{%
\section{Statistical Analysis Skills}\label{statistical-analysis-skills}}

\hypertarget{analyses}{%
\subsection{Analyses}\label{analyses}}

\begin{itemize}
\tightlist
\item
  Machine learning

  \begin{itemize}
  \tightlist
  \item
    \emph{Deep learning: CNN, RNN/LSTM, GAN}
  \item
    \emph{MVPA: SVM, Ridge, Lasso, Naive Bayes, Neural Networks/MLP}
  \end{itemize}
\item
  Bayesian Statistics

  \begin{itemize}
  \tightlist
  \item
    \emph{regression, model-building/comparison, bayes factors}
  \end{itemize}
\item
  Multilevel/mixed effects modeling
\item
  Structural Equation Modeling

  \begin{itemize}
  \tightlist
  \item
    \emph{EFA, single/multi-group CFA, path, latent growth, IRT}
  \end{itemize}
\item
  meta-analytic techniques

  \begin{itemize}
  \tightlist
  \item
    \emph{traditional RE/FE, bayesian multilevel estimation, p-value distribution analysis}
  \end{itemize}
\item
  GLM

  \begin{itemize}
  \tightlist
  \item
    \emph{simultaneous/hierarchical/mediation/moderation/logistic regression, AN/ANC/MAN/MANC-OVA}
  \end{itemize}
\end{itemize}

\hypertarget{languages-and-software-for-statistical-analysis}{%
\subsection{Languages and Software for statistical analysis}\label{languages-and-software-for-statistical-analysis}}

\begin{itemize}
\tightlist
\item
  Statistical Analyses: Python, R, MATLAB, JASP
\item
  Neuroimaging processing: Python, FSL, AFNI, ANTs
\item
  Software package development: MOTE (\url{https://cran.r-project.org/web/packages/MOTE/index.html})
\end{itemize}

\hypertarget{languages-and-software-for-stimulus-presentation}{%
\subsection{Languages and Software for Stimulus Presentation}\label{languages-and-software-for-stimulus-presentation}}

\begin{itemize}
\tightlist
\item
  Python (\emph{Psychopy}), MATLAB (\emph{Cogent})
\end{itemize}

\hypertarget{relevant-work-experience}{%
\section{Relevant Work Experience}\label{relevant-work-experience}}

\detailedsection{\detaileditem{University of Missouri}{Spring 17 - Current}{Research Assistant}{Columbia, MO}{\item{Research Assistant under Dr. David Geary.}\item{data collection, individual cognitive testing in Columbia Public School System}\item{data analysis, mauscript preparation}}\detaileditem{University of Missouri}{Fall 17 - Current}{Teaching Assistantship}{Columbia, MO}{\item{Teaching assistantship including grading, course content distribution, and course management}}\detaileditem{SKYfactor}{Spring 17 - Summer 17}{Data Science Intern}{Springfield, MO}{\item{data screening, cleaning, analysis, presentations for educational testing and research}\item{model building and data visualization}}\detaileditem{Missouri State University}{Fall 16 - Spring 17}{Teaching Assistantship}{Springfield, MO}{\item{teaching and management of Experimental Psychology lab courses}}\detaileditem{Missouri State University}{Fall 15 - Spring 16}{Graduate Assistantship}{Springfield, MO}{\item{management of online courses, course content management and distribution}\item{assisted in survey construction, data analysis, and literature reviews}}}

\hypertarget{service}{%
\section{Service}\label{service}}

Web \& Scholary Communications Committee (08/01/2018 - Present)

Ad-hoc Reviewer: \emph{Memory}; \emph{Brain \& Behavior}; \emph{Journal of Integrative Neuroscience}; \emph{Cognition and Emotion}; \emph{Psychology \& Aging}; \emph{Psychiatry Research}; \emph{Journal of Child Psychology \& Psychiatry}; \emph{Evolutionary Psychological Science}; \emph{The Social Sciences Journal}

\hypertarget{organizations-associations}{%
\section{Organizations / Associations}\label{organizations-associations}}

Psychonomic Society

Cognitive Neuroscience Society

American Psychological Assoication

Southwestern Psychological Association

\hypertarget{honors-awards}{%
\section{Honors / Awards}\label{honors-awards}}

Research Travel Award, \$900 cumulative, University of Missouri

Graduate College Research Grant, \$300, Missouri State University

Cum Laude, Missouri State University / Truman State University

President's List, Missouri State University / Truman State University / Benedictine College

Varsity Collegiate Baseball, Truman State University, Benedictine College

GLVC Academic all-conference team 2013-2014 \& 2014-2015, Truman State University

BCIA certification of HRV biofeedback, Truman State University

\end{document}
